Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-22 paper/tex/discussion.tex
remove SRM sentence
address final batch of Seth comments

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward a photometric redshift estimator that will be employed for LSST analyses.
Here we discuss the next steps for subsequent investigations.

@@

% Finally, while this paper and future papers discussed above focus on photometric redshift codes and estimating accurate \pzpdf s from training data, we plan a separate, but complementary, project to examine calibration of the resultant redshifts via spatial cross-correlations \citep{Newman:2008}, which will be explored in a separate series of future papers.
The overarching plan describing everything laid out in this section is described in more detail in the \lsstdesc\ Science Roadmap (see Footnote in Section~\ref{sec:intro}).

>>>>

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward a photometric redshift estimator that will be employed for LSST analyses.  Extensions of the experimental design will require further rounds of analyses, and the authors welcome interest from those outside \lsstdesc\ to have their codes assessed in these future investigations.
%Here we discuss the next steps for subsequent investigations.

@@

% Finally, while this paper and future papers discussed above focus on photometric redshift codes and estimating accurate \pzpdf s from training data, we plan a separate, but complementary, project to examine calibration of the resultant redshifts via spatial cross-correlations \citep{Newman:2008}, which will be explored in a separate series of future papers.
%The overarching plan describing everything laid out in this section is described in more detail in the \lsstdesc\ Science Roadmap (see Footnote in Section~\ref{sec:intro}).

### 2019-11-22 paper/tex/results.tex
address final batch of Seth comments

We begin with a demonstrative visual inspection of the \pzpdf s produced by each code for individual galaxies.
Figure~\ref{fig:pz_examples} shows the \pzpdf s for four galaxies chosen as examples of \pzpdf\ archetypes: a narrow unimodal PDF, a broad unimodal PDF, a bimodal PDF, and a multimodal PDF.
We reiterate that under our idealized experimental conditions, differences between codes are the isolated signature of the implicit prior due to the method by which the \pzpdf s were derived.

>>>>

We begin with a demonstrative visual inspection of the \pzpdf s produced by each code for individual galaxies.
Figure~\ref{fig:pz_examples} shows the \pzpdf s for four galaxies chosen as examples of \pzpdf\ archetypes: a narrow unimodal PDF, a broad unimodal PDF, a bimodal PDF, and a multimodal PDF.
We reiterate that under our idealized experimental conditions, differences between the resulting \pzpdf s are the isolated signature of the implicit prior due to the method by which the \pzpdf s were derived.
